---
title: "Lecture 11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r}

# Download some example PDB files
library(bio3d)
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
files <- get.pdb(ids, split = TRUE)

# Extract and align the chains we are interested in
pdbs <- pdbaln(files, fit = TRUE)
# Print to screen a summary of the 'pdbs' object
pdbs

# Access the first 5 rows, and 8 columns
pdbs$ali[1:5, 1:8]
# Associated residues numbers
pdbs$resno[1:5, 1:8]

# Inspect alignment for gaps
gaps <- gap.inspect(pdbs$ali)
# Indices of non-gap columns
head(gaps$f.inds)
# Access non-gap columns
pdbs$ali[, gaps$f.inds]
# Calculate sequence identity
seqidentity(pdbs)

# Calculate RMSD
rmsd(pdbs)

# Calculate RMSD
rd <- rmsd(pdbs)
# Clustering
hc <- hclust(as.dist(rd))
grps <- cutree(hc, k=3)
# Plot results as dendrogram
hclustplot(hc, k=3)

# Perform PCA
pc <- pca(pdbs)
plot(pc, col=grps)
# NMA all structures
modes <- nma(pdbs)
plot(modes, pdbs, col=grps, spread=TRUE)
#tar -xvf muscle.darwin
#mv muscle .darwin/usr/local/bin/muscle

#tar (tape archive)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
